New orbits of irregular satellites based on thousands of new observations and predictions for stellar occultations up to 2020

### 2016-06-22 Irregular-occ/Irregular-occ.tex
.

Our numerical model describes the dynamical evolution of the irregular satellites of Jupiter in a jovicentric reference frame. The satellites are submitted to the influence of the Sun and the rest of the solar system, as well as that of the Galilean satellites and the first harmonics of Jupiter's gravity field. The axes of the reference frame are those of the ICRS.

We use the following notations:
\begin{itemize}
\item $i$ and $l$ one of the irregular satellites of Jupiter
\item $J$ Jupiter 
\item $j$ another body of the Solar System
\item $M_j$ the mass of the $j$-th body, not an irregular satellite
\item $m_i$ the mass of the irregular satellite $i$
\item $\vec{r_i}$ the position of the $i$-th body with respect to the barycentre of Jupiter System
\item $r_{ij}$ the distance between bodies $i$ and $j$  
\item $R_J$ the radius of Jupiter
\item $J_n$ the dynamic polar oblateness of the n-th order for Jupiter's gravity field
\item $U_{\bar{l}\hat{J}}$ potential generated by the oblateness of Jupiter on the satellite $l$
\item $\Phi_i$ is the inclination of the $i$-th satellite with respect to Jupiter's equator.
\end{itemize}

For an irregular satellite $i$, under the gravitational influence of Jupiter, the $\mathcal{N}-1$ other irregular satellites, the regular Jovian satellites and the rest of the Solar System ($\mathcal{N}$ bodies), the equation of motion is:
\begin{equation}\begin{array}{ll}

\ddot{\vec{r_i}}= & \displaystyle -GM_J\frac{\vec{r_J}-\vec{r_i}}{r_{iJ}^3}-\sum_{l=1,l\neq i}^\mathcal{N'}Gm_l\frac{\vec{r_l}-\vec{r_i}}{r_{il}^3}\\
&\displaystyle -\sum_{j=1}^\mathcal{N}GM_j \left(\frac{\vec{r_j}-\vec{r_i}}{r_{ij}^3} - \frac{\vec{r_j}-\vec{r_J}}{r_{Jj}^3} \right)\\
 & \displaystyle +GM_J \nabla U_{\bar{l}\hat{J}} -\sum_{l=1}^\mathcal{N} Gm_l\nabla U_{\bar{l}\hat{J}}
\end{array}
\label{Eq:1}
\end{equation}
where the last term in the brackets and the last term in Eq. \ref{Eq:1} represent undirect perturbations. The oblateness potential seen by the body $i$ because of Jupiter is:
\begin{equation}\begin{array}{ll}

U_{\bar{l}\hat{J}}=&\displaystyle -\frac{R_J^2 J_2}{r_{iJ}^3}\left(\frac{3}{2}\sin^2 \Phi_i-\frac{1}{2}\right)\\ &\\ & 
\displaystyle-\frac{R_J^4 J_4}{r_{iJ}^5}\left(\frac{35}{8}\sin^4 \Phi_i-\frac{15}{4}\sin^2 \Phi_i+\frac{3}{8}\right)\\
& \\
&\displaystyle-\frac{R_J^6 J_6}{r_{iJ}^7}\left(\frac{231}{16}\sin^6 \Phi_i-\frac{315}{16}\sin^4 \Phi_i+\frac{105}{16}\sin^2 \Phi_i-\frac{5}{16}\right)

@@

The expressions of $\nabla_lU_{\bar{l}\, \hat{i}}$ and $\nabla_i U_{\bar{i}\, \hat{l}}.$ have been developed in \citet{Lainey2004}. The equations of motion are integrated with the numerical integrator RADAU \citep{Everhart1985}. 
Our model was fitted to the observations through a least-squares procedure. The satellites were integrated one dynamical family at a time, to gain computing time, while losing minimum precision. Indeed, the interactions between satellites not belonging to the same dynamical family are negligible considering the short timespan of our integration.

>>>>

Our numerical model describes the dynamical evolution of the irregular satellites of Jupiter in a jovicentric reference frame. The satellites are submitted to the influence of the Sun and the \textbf{main bodies of the solar system (from Mercury to Pluto, plus the Moon)}, as well as those of the Galilean satellites and the first harmonics of Jupiter's gravity field. The axis of the reference frame are \textbf{expected to be those of the equatorial reference frame J2000}.

We use the following notations: \begin{itemize}
\item \textbf{in one dynamical family consisting of $\mathcal{N}$ irregular satellites, $i$ will stand for the one whose equation of motion we are considering, $l$ will stand for another irregular satellite in gravitationnal interaction belonging to the same family}
\item $J$ Jupiter
\item $j$ another body of the Solar System, \textbf{among the 10 included (Sun+planets+Pluto+Moon)}
\item $M_j$ the mass of the $j$ body, not an irregular satellite
\item $m_i$ the mass of the irregular satellite $i$
\item $\vec{r_i}$ the position of the $i$ body with respect \textbf{to the center of Jupiter}
\item $r_{ij}$ the distance between bodies $i$ and $j$
\item $R_J$ the radius of Jupiter
\item $J_n$ the dynamic polar oblateness of the nth order for Jupiter's gravity field
\item $U_{\bar{l}\hat{J}}$ potential generated by the oblateness of Jupiter on the satellite $l$
\item $\Phi_i$ is the latitude of the $i$ satellite with respect to Jupiter's equator.
\end{itemize}

For an irregular satellite $i$, under the gravitational influence of Jupiter, the \textbf{seven other irregular satellites}, the regular Jovian satellites and\textbf{ the main bodies of the Solar System}, the equation of motion is:
\begin{equation}
\label{Eq:eq1}
\begin{array}{ll}

\ddot{\vec{r_i}}= & \displaystyle -GM_J\frac{\vec{r_J}-\vec{r_i}}{r_{iJ}^3}-\sum_{l=1,l\neq i}^\mathcal{N} Gm_l\frac{\vec{r_l}-\vec{r_i}}{r_{il}^3}\\
&\displaystyle -\sum_{j=1}^{10}GM_j \left(\frac{\vec{r_j}-\vec{r_i}}{r_{ij}^3} - \frac{\vec{r_j}-\vec{r_J}}{r_{Jj}^3} \right)\\
 & \displaystyle +GM_J \nabla U_{\bar{i}\hat{J}} -\sum_{l=1}^\mathcal{N} Gm_l\nabla U_{\bar{l}\hat{J}}
\end{array}
\end{equation}

where the last term in brackets and the last term in Eq. \ref{Eq:eq1} represent undirect perturbations. The oblateness potential seen by \textbf{a satellite $i$ because of Jupiter is (with a similar expression for the oblateness seen by a satellite $l$)}:
\begin{equation}\begin{array}{ll}

U_{\bar{i}\hat{J}}=&\displaystyle -\frac{R_J^2 J_2}{r_{iJ}^3}\left(\frac{3}{2}\sin^2 \Phi_i-\frac{1}{2}\right)\\ &\\ &
\displaystyle-\frac{R_J^4 J_4}{r_{iJ}^5}\left(\frac{35}{8}\sin^4 \Phi_i-\frac{15}{4}\sin^2 \Phi_i+\frac{3}{8}\right)\\
& \\
&\displaystyle-\frac{R_J^6 J_6}{r_{iJ}^7}\left(\frac{231}{16}\sin^6 \Phi_i-\frac{315}{16}\sin^4 \Phi_i+\frac{105}{16}\sin^2 \Phi_i-\frac{5}{16}\right)

@@

\textbf{The expressions of $\nabla U$ have been developed in \cite{Lainey2004}}. \textbf{The equations of motion are integrated with the 15th order numerical integrator RADAU \citep{Everhart1985} using a constant step of one day}. \textbf{The positions of the objects of the solar system are provided by the DE423 ephemeris \citep{Folkner2010}, while those of the galilean satellites are provided by NOE2010 \citep{Lainey2004}}.
Our model was fitted to the observations through a least-squares procedure. The satellites were integrated one dynamical family at a time, to gain computing time, while losing minimum precision. Indeed, the interactions between satellites not belonging to the same dynamical family are negligible considering the short timespan of our integration.
